Supplementary information for The transboundary nature of the world’s exploited marine species

### 2020-10-14 Scripts/supplements.Rmd
solve issues on merging

---
title: "Supplementary information for The transboundary nature of the world’s exploited marine species"
author: "Authors: Juliano Palacios-Abrantes, Gabriel Reygondeau, Colette C.C. Wabnitz and William W.L. Cheung"
output: pdf_document
header-includes: #allows you to add in your own Latex packages
- \usepackage{float} #use the 'float' package
- \floatplacement{figure}{H} #make every figure with caption = h
- \floatplacement{table}{H}
- \usepackage{caption}
- \captionsetup[figure]{name= Figure S}
- \captionsetup[table]{name= Table S}
---

```{r setup, eval = T, echo=F, warning=F,message=F, results='hide'}

@@

The number of grid cells in which a species is present (*Area Index*) is expected to directly influence whether or not a species is considered transboundary. Therefore, we tested the sensitivity of our results to the *Area Index* by estimating the number of transboundary species along a gradient of values (Supplementary Fig. S3). As expected, using a more relaxed value (e.g. the species is present within 10% or more of the EEZ) will result in a greater number of transboundary species (median of 40 EEZs shared per species), while a more restrictive value (e.g., 50%) results in a median estimate of 4. The current analysis utilized a 25% *Area Index* threshold (Supplementary Fig. S3 - darker histogram).

```{r Call_Sup3, eval = T, fig.width=6, fig.height=9, echo=FALSE, fig.pos= "H", fig.cap="Histogram of number of transboundary species using different Area Index threshold values. The darker histogram represents the threshold (25%) used in the present analysis. Figure created using R version 3.5.2."}

img <- readPNG("../Figures/FigS3.png")
grid.raster(img)
```

@@

# Supplementary Tables

```{r Call_SupT_1, eval = T, echo = F, fig.pos= "H"}

read.csv("~/GitHub/FishForVisa/Tables/Table_S1.csv") %>% 
  clean_names() %>% 
  filter(sub_region != "Other") %>% 
  arrange(sub_region) %>% 
  rename("UN sub region" = sub_region,
         "Area of EEZs (Km^2)" = size_entity_sum) %>% 
  kable("latex",
        booktabs = T,
        caption= "Size of all the EEZs in each sub region determined by the United Nations") %>% 
  kable_styling(full_width = T)

@@

# Translated Abstacts

## Español

Es frecuente que los límites de las herramientas de manejo ambiental y la distribución de especies no coincidan como sucede en el caso de especies marinas que cruzan múltiples Zonas Económicas Exclusivas (ZEE). Este tipo de movimiento representa un desafío para el manejo pesquero, ya que las políticas públicas tienden a enfocarse en el nivel nacional; sin embargo, es necesario establecer colaboraciones internacionales para maximizar los beneficios ecológicos, sociales y económicos a largo plazo obtenidos con la captura de especies marinas compartidas. En este artículo se combinó la distribución de especies con la delimitación espacial de las ZEE para identificar el número de especies marinas explotadas comercialmente que son compartidas por naciones vecinas (especies transfronterizas). Los resultados revelaron que el 67% de las especies analizadas pertenecen a esa categoría (n = 633). Entre 2005 y 2014, las pesquerías que tenían como objetivo estas especies y que operaban dentro de las ZEE mundiales capturaron un promedio de 48 millones de toneladas por año, lo que equivale a un promedio de 77 mil millones de dólares en ingresos anuales por pesca. Durante este tiempo, más del 90% de las capturas y beneficios económicos de algunos países fue resultado de unos pocos recursos compartidos. Así mismo, se demuestra que las capturas de especies transfronterizas están disminuyendo a un ritmo mayor que las no transfronterizas. Este estudio tiene implicaciones directas para el manejo pesquero de dichas especies, destacando la necesidad de fortalecer una cooperación internacional eficiente y equitativa.

## Portugues

É frequente que os limites dos instrumentos de gestão de recursos naturais e a distribuição das espécies não coincidam como acontece no caso das espécies marinhas que cruzam múltiplas Zonas Econômicas Exclusivas (ZEE). Este tipo de movimento representa um desafio para a gestão pesqueira, já que as políticas públicas tendem a ser focadas ao nível nacional; portanto, colaborações internacionais precisam ser estabelecidas para maximizar os benefícios ecológicos, sociais e econômicos de longo prazo alcançados com a captura de espécies marinhas compartilhadas. Neste artigo, a distribuição das espécies foi combinada com a delimitação espacial de ZEEs para identificar o número de espécies marinhas exploradas comercialmente que são compartilhadas por nações vizinhas (espécies transfronteiriças). Os resultados revelaram que 67% das espécies analisadas pertencem a essa categoria (n = 633). Entre 2005 e 2014, as pescarias que operavam nas ZEEs globais que visam essas espécies capturaram uma média de 48 milhões de toneladas por ano, o que equivale a uma média de $ 77 bilhões em receitas anuais de pesca. Durante este tempo, mais de 90% das capturas e benefícios econômicos de alguns países foi resultado de alguns recursos compartilhados. Da mesma forma, se mostra que as capturas de essas espécies estão diminuindo a um ritmo maior do que as das não transfronteiriças. Este estudo tem implicações diretas para a gestão da pesca de espécies referidas, destacando a necessidade de fortalecer uma cooperação internacional eficiente e equitativa.

## Françuais

>>>>

---
output:
  bookdown::pdf_book:
    toc : no
    keep_tex: no
    number_sections: yes
header-includes: #allows you to add in your own Latex packages
- \usepackage{float} #use the 'float' package
- \floatplacement{figure}{H} #make every figure with caption = h
- \floatplacement{table}{H}
- \usepackage{caption}
---

```{r setup_sup, eval = T, echo=F, warning=F,message=F, results='hide'}

@@

The number of grid cells in which a species is present (*Area Index*) is expected to directly influence whether or not a species is considered transboundary. Therefore, we tested the sensitivity of our results to the *Area Index* by estimating the number of transboundary species along a gradient of values (Figure \@(fig:CallSup3)). As expected, using a more relaxed value (e.g. the species is present within 10% or more of the EEZ) will result in a greater number of transboundary species (median of 40 EEZs shared per species), while a more restrictive value (e.g., 50%) results in a median estimate of 4. The current analysis utilized a 25% *Area Index* threshold (Figure \@(fig:CallSup3 - darker histogram).

```{r CallSup3, eval = T, fig.width=6, fig.height=9, echo=FALSE, fig.pos= "H", fig.cap=" Histogram of number of transboundary species using different Area Index threshold values. The darker histogram represents the threshold (25%) used in the present analysis. Figure created using R version 3.5.2."}

img <- readPNG("../Figures/FigS3.png")
grid.raster(img)

@@

```{r TableS1, eval = T, echo = F}

read.csv("../Tables/Table_S1.csv") %>% 
  clean_names() %>% 
  filter(sub_region != "Other") %>% 
  arrange(size_entity_sum) %>% 
  rename("UN sub region" = sub_region,
         "Area of EEZs (Km^2)" = size_entity_sum) %>% 
  kable("latex",
        booktabs = T,
        caption= "Size of all the EEZs in each sub region determined by the United Nations") %>% 
  kable_styling(full_width = T)

@@
